\section*{Referências}

\begin{enumerate}
  \item K. Deb, A. Pratap, S. Agarwal, T. Meyarivan. \textit{A fast and elitist multiobjective genetic algorithm: NSGA-II}. IEEE Transactions on Evolutionary Computation, 6(2):182-197, 2002.
  
  \item K. Deb. \textit{Multi-Objective Optimization using Evolutionary Algorithms}. John Wiley \& Sons, Chichester, UK, 2001.
  
  \item E. Zitzler, K. Deb, L. Thiele. \textit{Comparison of Multiobjective Evolutionary Algorithms: Empirical Results}. Evolutionary Computation, 8(2):173-195, 2000.
  
  \item H. Ishibuchi, N. Tsukamoto, Y. Nojima. \textit{Evolutionary many-objective optimization: A short review}. IEEE Congress on Evolutionary Computation, pp. 2419-2426, 2008.
  
  \item R. C. Purshouse, P. J. Fleming. \textit{On the Evolutionary Optimization of Many Conflicting Objectives}. IEEE Transactions on Evolutionary Computation, 11(6):770-784, 2007.
  
  \item K. Deb, H. Jain. \textit{An Evolutionary Many-Objective Optimization Algorithm Using Reference-Point-Based Nondominated Sorting Approach, Part I: Solving Problems With Box Constraints}. IEEE Transactions on Evolutionary Computation, 18(4):577-601, 2014.
  
  \item Q. Zhang, H. Li. \textit{MOEA/D: A Multiobjective Evolutionary Algorithm Based on Decomposition}. IEEE Transactions on Evolutionary Computation, 11(6):712-731, 2007.
  
  \item N. Beume, B. Naujoks, M. Emmerich. \textit{SMS-EMOA: Multiobjective selection based on dominated hypervolume}. European Journal of Operational Research, 181(3):1653-1669, 2007.
  
  \item E. Zitzler, L. Thiele. \textit{Multiobjective evolutionary algorithms: a comparative case study and the strength Pareto approach}. IEEE Transactions on Evolutionary Computation, 3(4):257-271, 1999.
  
  \item A. J. Nebro, J. J. Durillo, M. Vergne. \textit{Redesigning the jMetal Multi-Objective Optimization Framework}. GECCO '15 Companion, pp. 1093-1100, 2015.
\end{enumerate}
